### 2020-09-17 manuscript/ERL_global_C_review.Rmd
Update ERL_global_C_review.Rmd

**Authors:** 
Kristina J. Anderson-Teixeira^1,2^*

@@

*Review Results/ Synthesis.*  The rate of C cycling generally increased from boreal to tropical regions, whereas C stocks showed less directional variation. The majority of flux variables, together with most live biomass pools, increased significantly with stand age, and the rate of increase again tended to increase from boreal to tropical regions.

*Discussion.* *[Discussion section will interpret results, highlighting new and significant findings, and discuss implications. Tentative headings are “Stand level C cycling in forests globally”, “Age trends in C cycling”, and “Implications for climate change mitigation”.]*

@@

Here, we synthesize ForC data to provide a macroscopic overview of stand-level carbon cycling of the world’s major forest biomes and how it varies with stand age. We address two broad questions:

1. How do C cycling vary across the worlds major forest biomes (*i.e.*, tropical, temperate broadleaf and deciduous, boreal)?

2. How does C cycling vary with stand age?

@@

Carbon cycling rates generally increased from boreal to tropical regions and with stand age. Specifically, the major C fluxes were highest in tropical forests, intermediate in temperate (broadleaf or conifer) forests, and lowest in boreal forests—a pattern that generally held for regrowth as well as mature forests (Figs. 6-7). In contrast to C fluxes, there was little directional variation in mature forest C stocks across biomes (Figs. 2-5, 7). The majority of flux variables, together with most live biomass pools, increased significantly with stand age (Figs. 6-7). Together, these results indicate that, moving from cold to tropical climates and from young to old stands, there is a general acceleration of C cycling, whereas C stocks of mature forests are influenced by a different set of drivers.

@@

@@

### Acknowledgements
All researchers whose data is included in ForC and this analysis.
Thanks to Norbert Kunert for helpful discussion.
A Smithsonian Scholarly Studies grant to KAT and HML.

>>>>

**Authors:**

Kristina J. Anderson-Teixeira^1,2^*

@@

*Review Results/ Synthesis.*  ForC v.XX yielded a fairly comprehensive picture of C cycling in the world's major forest biomes, with broad closure of C budgets. The rate of C cycling generally increased from boreal to tropical regions, whereas C stocks showed less directional variation. The majority of flux variables, together with most live biomass pools, increased significantly with stand age, and the rate of increase again tended to increase from boreal to tropical regions.

*Discussion.* This analysis yields a comprehensive, largely consistent picture of C cycling across the world's forests.   *[Discussion section will interpret results, highlighting new and significant findings, and discuss implications. Tentative headings are “Stand level C cycling in forests globally”, “Age trends in C cycling”, and “Implications for climate change mitigation”.]*

@@

Here, we synthesize ForC data to provide a macroscopic overview of stand-level carbon cycling of the world’s major forest biomes and how it varies with stand age. We address three broad questions:

1. To what extent can we fully represent, and "close", C budgets for each of the world's major forest biomes (*i.e.*, tropical, temperate broadleaf and deciduous, boreal) based on the current ForC data?

2. How do C cycling vary across the worlds major forest biomes?

3. How does C cycling vary with stand age?

@@

ForC v.XX yielded a fairly comprehensive picture of C cycling in the world's major forest biomes. 
Carbon cycling rates generally increased from boreal to tropical regions and with stand age. 
Specifically, the major C fluxes were highest in tropical forests, intermediate in temperate (broadleaf or conifer) forests, and lowest in boreal forests -- a pattern that generally held for regrowth as well as mature forests (Figs. 6-7). 
In contrast to C fluxes, there was little directional variation in mature forest C stocks across biomes (Figs. 2-5, 7). 
The majority of flux variables, together with most live biomass pools, increased significantly with stand age (Figs. 6-7). 
Together, these results indicate that, moving from cold to tropical climates and from young to old stands, there is a general acceleration of C cycling, whereas C stocks of mature forests are influenced by a different set of drivers.

*C variable coverage and budget closure*

Coverage:

* We have fairly good coverage of most major variables
* (note how this improves upon previous data compilations/ for which variables does ForC make the greatest difference (e.g., not AGB or NEE/GPP/Reco, but by far the latest data compilation for dead wood, [variables])
* Noteable holes include: fluxes: R_auto_ag, woody mortality, folivary/ herbivory and respiration of herbivores (and therefore total R_het), ANPP_repro; also fluxes in tropical regrowth forests
* for the C stocks considered here, the most poorly covered is dead wood (none in E hemisphere!), despite a focused effort on this variable that has resulted in ForC being by far the largest collection of these data.
* all variables poorly covered in Africa

Thus, overall, we're lacking coverage of fluxes to herbivores and higher consumers, along with the woody mortality and dead wood.

Closure:

* C cycle closure is fairly good. 
* However, SD's are often large, reflective of significant within-biome variation. This makes the standard for closure relatively loose.
* Lack of closure, in the few instances where it occurs, is probably more reflective of differences in the representation of forest types (e.g., disproportionate representation of US Pacific NW for aboveground woody biomass relative to AGB; Fig. 3) than of methodological accuracy.

Thus, overall, a high degree of closure implies that ForC gives a consistent picture of C cycling within biomes. 
While these means are unlikely to be accurate representations of C cycling within any particular forest, they provide a useful baseline for comparison.

@@

@banbury_morgan_global_nodate

@@

*Relevance for climate change modeling and mitigation*

Importance of forest C in climate change modeling and mitigation...

For C can help models by serving as benchmark data.
* (cite Dietze paper that we reviewed)

For some variables, such as AGB of mature forests, we sources other than ForC can provide the best available data.
However, for others, ForC provides by far the most comprehensive source:
* agb age trends (GROA; Cook-Patton et al. 2020)
* dead wood (cite need for this)
* fluxes

### Acknowledgements
All researchers whose data is included in ForC and this analysis.
Thanks to Norbert Kunert and [Helene's intern] for helpful input at an earlier phase.
A Smithsonian Scholarly Studies grant to KAT and HML.

### References
